\sysfull

### 2017-08-02 paper/intro.tex
cutting text in the intro

While promising, energy-harvesting devices present a unique design challenge in that they operate only {\em intermittently} when energy is available~\cite{hicks_isca_2017,lucia_snapl_2017}. An
energy-harvesting device buffers energy from its environment, e.g., in a capacitor~\cite[Fig. 3]{gorlatova_tmc_2013},~\cite[Fig. 1]{gunduz_commag_2014}. When a threshold quantity of energy accumulates, the device begins operating. Harvestable energy sources typically produce relatively very little power compared to a platform's operating power level---compare for instance~\cite[Table III and V]{prasad_comst_2014} with~\cite[Table I]{carrano_cst_2014}. A devices operates for a brief period of time and when buffered energy is depleted, shuts down and begins recharging to operate again later. As an example, inter-task time may even exceed 20\,s for wireless energy-harvesting battery-less vivo digestive tract monitoring system~\cite[Fig. 3c]{nadeau_naturebio_2017}. On top of that, charge and discharge times vary by device and some of them~\cite{wisp} may fail $\approx$10 to $\approx$100 times per second~\cite[Fig. 1]{tan_infocom_2016},~\cite[Fig. 1]{mementos},~\cite[Fig. 3]{nvp}.

>>>>

While promising, energy-harvesting devices present a unique design challenge in that they operate only {\em intermittently} when energy is available~\cite{hicks_isca_2017,lucia_snapl_2017}. An
energy-harvesting device buffers energy from its environment, e.g., in a capacitor~\cite[Fig. 3]{gorlatova_tmc_2013},~\cite[Fig. 1]{gunduz_commag_2014}. When a threshold quantity of energy accumulates, the device begins operating. Harvestable energy sources typically produce little power compared to a platform's operating power level---compare for instance~\cite[Table III and V]{prasad_comst_2014} with~\cite[Table I]{carrano_cst_2014}. A devices operates for a brief period of time and when buffered energy is depleted, shuts down and begins recharging to operate again later. As an example, inter-task time may even exceed 20\,s for wireless energy-harvesting battery-less vivo digestive tract monitoring system~\cite[Fig. 3c]{nadeau_naturebio_2017}. On top of that, charge and discharge times vary by device and some of them~\cite{wisp} may fail $\approx$10 to $\approx$100 times per second~\cite[Fig. 1]{tan_infocom_2016},~\cite[Fig. 1]{mementos},~\cite[Fig. 3]{nvp}.
